The Habitable Zone Inner Edge Discontinuity: Probing the Imprint of Runaway Greenhouse Climates on Exoplanet Demographics

### 2023-04-19 src/tex/ms.tex
address minor comments

\subsection{Stellar luminosity evolution}
Planetary systems are hosted by stars of a wide range of ages, and stellar luminosities evolve with time.
Since the emergence of a runaway greenhouse phase on a planet is highly dependent on the level of radiation it receives, and thus on the luminosity of the host star, we assigned age-dependent luminosities to our synthetic stars.

@@

Other missions have been proposed that focus on characterizing exoplanet habitability, most notably the \hwo\ concept, which will build on the two precursor direct imaging concepts LUVOIR~\citep{LUVOIR2019} and HabEx~\citep{Gaudi2020c}.
Similar science objectives are pursued by the Large Interferometer For Exoplanets~\citep[\life,][]{Quanz2021}, a mission concept utilizing a space-based mid-infrared nulling interferometer.
Direct imaging surveys do not directly measure planetary radii and are primarily useful for providing context through atmospheric measurements of individual planets.
However, because mid-infrared retrievals do not suffer from the degeneracy between cloud albedo and changes in surface area, the planet radius can be retrieved in mid-infrared wavelengths~\citep{2018ExA....46..543D,2021ExA...tmp..118Q}.
Mid-infrared direct imaging techniques, in particular, enable to study much deeper atmospheric layers than possible in reflected light~\citep{Wordsworth2022}.
Hence, the atmospheric structure can be retrieved for a wider variety of thermal and atmospheric scenarios.\todo[inline]{ (Konrad+, Alei+). CITE}
Finally, since the peak thermal emission in super-runaway climates will substantially decrease the star-to-planet flux ratio, mid-infrared wavelengths offer the possibility to probe the diversity of super-runaway climates in systems across different ages~\citep{2014ApJ...784...27L,2019A&A...621A.125B}.
With a sample size of a few tens of planets crossing the runaway greenhouse transition, direct imaging missions will thus enable key insights into the compositional inventory of atmospheric volatiles and climate states~\citep{2021exbi.book....5H,2022arXiv220505696C}, adding important details to a potential runaway greenhouse detection purely via transit radii.

>>>>

\subsection{Stellar luminosity evolution}
Planetary systems are hosted by stars of a wide range of ages, and stellar luminosities evolve with time.
Since the presence of a runaway greenhouse state is highly dependent on the amount of radiation received by the planet, and thus on the luminosity of the host star, we assigned age-dependent luminosities to our synthetic stars.

@@

Other missions have been proposed that focus on characterizing exoplanet habitability, most notably the \hwo\ concept, which will build on the two precursor direct imaging concepts LUVOIR~\citep{LUVOIR2019} and HabEx~\citep{Gaudi2020c}.
Similar science objectives are pursued by the Large Interferometer For Exoplanets~\citep[\life,][]{Quanz2021}, a mission concept utilizing a space-based mid-infrared nulling interferometer.
Direct imaging surveys do not directly measure planetary radii and are primarily useful for providing context through atmospheric measurements of individual planets.
However, because mid-infrared retrievals do not suffer from the degeneracy between cloud albedo and changes in surface area, the planet radius can be retrieved in mid-infrared wavelengths~\citep{2018ExA....46..543D,2021ExA...tmp..118Q}.
Mid-infrared direct imaging techniques, in particular, enable to study much deeper atmospheric layers than possible in reflected light~\citep{Wordsworth2022}.
Hence, the atmospheric structure can be retrieved for a wider variety of thermal and atmospheric scenarios.\todo[inline]{TIM: what papers by Konrad+, Alei+ did you want to cite here?}
Finally, since the peak thermal emission in super-runaway climates will substantially decrease the star-to-planet flux ratio, mid-infrared wavelengths offer the possibility to probe the diversity of super-runaway climates in systems across different ages~\citep{2014ApJ...784...27L,2019A&A...621A.125B}.
With a sample size of a few tens of planets crossing the runaway greenhouse transition, direct imaging missions will thus enable key insights into the compositional inventory of atmospheric volatiles and climate states~\citep{2021exbi.book....5H,2022arXiv220505696C}, adding important details to a potential runaway greenhouse detection purely via transit radii.
